On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-04-16 manuscripts/PNAS/chazthm_pnas.tex
problem 2 typo

\begin{problem}\label{OptimizationProblem}
Find a matrix $\mathbf{B} \in \mathbb{R}^{\bar m}$ and $k$-sparse $\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$ that solve:
\begin{align}\label{minsum}
\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$}.
\end{align}
\end{problem}

>>>>

\begin{problem}\label{OptimizationProblem}
Find a matrix $\mathbf{B} \in \mathbb{R}^{\bar m}$ and vectors \mbox{$\mathbf{\bar x}_1, \ldots, \mathbf{\bar x}_N \in \mathbb{R}^{\bar m}$} that solve:
\begin{align}\label{minsum}
\min \sum_{i = 1}^N \|\mathbf{\bar x}_i\|_0 \ \ 
\text{subject to} \ \ \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\bar x}_i\|_2 \leq \varepsilon, \ \text{for all $i$}.
\end{align}
\end{problem}
